\documentclass{article}

\usepackage{amsmath,amsthm,amssymb,bm}

\title{Bayesian Marked Spatial Point Process with Applications to
  Professional Basketball \\
\large Project Proposal}
\author{Jieying Jiao, Guanyu Hu}
\date{\today}

\begin{document}
\maketitle

Basketball data records the shoting data for each basketball
player. This includes the shoting location and time information, and
indicator showing made or miss. Previous studies focused on modeling
the location using spatial point process. Here we want to consider the 
accuracy of shot, i.e, whether this shot is made or miss. So we decide
to use marked spatial point process.


Possion process is a widely used parametric distribution for a finite
set of count variable. We use it to model the location part of shot. A
poisson process $\bm{Y} = (y(s_1),...,y(s_n))$ is a random countable subset
on $\mathcal{B} \subseteq \mathcal{R}^2$, where $s_i \in \mathcal{B},
i=1,\cdots,n$. Then for any areal $A\subseteq\mathcal{B}$, we define
the counting process $N_{\bm{Y}}(A)=\sum_{i=1}^n 1(s_i\in A)$. If the
poisson process $\bm{Y}$ has intensity function $\lambda(\bm{s})$,
then $N_{\bm{Y}}(A)\sim Poi(\lambda(A))$, where
$\lambda(A)=\int_A\lambda(s)ds$. Then the log-likelihood function on
$A$ is 	$l=\sum_{i=1}^n \text{log}\lambda(s_i)-\int_A \lambda(s)
ds$. Usually, we often has following regression form for the spatially
varying intensity:
$\lambda(s_i)=\lambda_0\exp(\bm{\beta}\bm{X_1}(s_i))$, where $\lambda_0$
is the baseline of intensity function, $\bm{\beta}$ is regression
coefficient, and $\bm{X_1}(s_i)$ is spatially varying covariates. 


For the marks part, we have binary variable, i.e, made or miss. So we
decide to use logistic regression to model marks, i.e, $m(s) \sim
Ber(p(s))$, $logit(p(s))=\alpha_0\lambda(s)+\bm{\alpha}\bm{X_2}(s)$,
where $\alpha_0, \bm{\alpha}$ are regression coefficients,
$\bm{X_2}(s_i)$ is spatially varying covariates. This is called
intensity dependent model.

Then we have the joint model likelihood for marked point process:
$$L =\prod_{i=1}^n p(m(s_i)|\lambda(s_i))\times
                \prod_{i=1}^n \lambda(s_i)\times \exp\left(-\int_A
                  \lambda(s)ds\right)$$
The prior distribution can be as follow: $\lambda_0 \sim
\text{G}(a_1,b_1), \bm{\beta} \sim \text{MVN}(0,\sigma^2I), \sigma^2
\sim \text{IG}(a_2,b_2), \bm{\alpha} \sim \text{MVN}(0,\delta^2I),
\tau^2 \sim \text{IG}(a_3,b_3), \delta^2 \sim \text{IG}(a_4,b_4).$


We also plan to conduct Bayesian model selection for real data and
simulation study.
\end{document}

